RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

pdf("test.pdf")
plotZenith(df)
dev.off()

```{r zenith.disease.mSigDB}
geneSets_MSigDB = get_MSigDB(c('H', "C1", "C2", "C3", "C5", "C7"))

@@

# Integrate CommonMind Consortium
```{r load.cmc}

geneCounts_CMC = readRDS(synGet('syn22416410')$path)
info_CMC = readRDS(synGet('syn22416411')$path)

>>>>

```{r zenith.disease.mSigDB, fig.width=12}
geneSets_MSigDB = get_MSigDB(c('H', "C1", "C2", "C3", "C5", "C7"))

@@

# Integrate CommonMind Consortium
```{r load.cmc}
geneCounts_CMC = readRDS(synGet('syn22416410')$path)
info_CMC = readRDS(synGet('syn22416411')$path)
```
